---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/nser)](https://cran.r-project.org/package=nser)
[![cran checks](https://cranchecks.info/badges/summary/nser)](https://cran.r-project.org/web/checks/check_results_nser.html)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable-1)
![Downloads](http://cranlogs.r-pkg.org/badges/nser)
[![](https://cranlogs.r-pkg.org/badges/grand-total/nser)](https://cran.r-project.org/package=nser)
[![Travis build status](https://travis-ci.com/nandp1/nser.svg?branch=main)](https://travis-ci.com/nandp1/nser)
[![R-CMD-check](https://github.com/nandp1/nser/workflows/R-CMD-check/badge.svg)](https://github.com/nandp1/nser/actions)
<!-- badges: end -->

# Introduction

"nser" helps you to download historical bhavcopy of Equities and F&O segment easily. 

Package website [nser](https://nandp1.github.io/nser/)

## New function ```bhavs``` to download Equity Bhavcopy zip file through RSelenium. 

## Installation

You can install "nser" from [CRAN](https://cloud.r-project.org/web/packages/nser/index.html) with:

``` r
install.packages("nser")
```
Install it from github by:
``` r
install.packages("devtools")
library(devtools)
install_github("nandp1/nser")
```

## Example 1. Downloading Historical Equity Bhavcopy 

```{r example}
library(nser)
# Download Bhavcopy of 1st July 2021
report1 = bhav("01072021")
```

## Example 2. Downloading Historical F&O Bhavcopy 

```{r example}
library(nser)
# Download Bhavcopy of 1st July 2021
report2 = fobhav("01072021")
```
## Example 3. Downloading today's Equity and F&O Bhavcopy 
```{r example}
library(nser)
report3 = bhavtoday()
report4 = fobhavtoday()
```

## Example 4. Live F&O data.
``` r
library(nser)
nselive()
```

## Example 5. Pre market open data of F&O stocks
``` r
library(nser)
nseopen("fo")
```

## Example 6. Current and Upcoming IPO's
``` {r example}
library(nser)
nseipo()
```

## Example 7. RSelenium to Download Equity Bhavcopy
``` r
library(nser)
library(RSelenium)

# Start a selenium server and browser
# For Google Chrome (Update Chrome to latest version)

 driver <- rsDriver(browser = c("chrome"), port = 3163L, chromever = "91.0.4472.101")
 remDr <- driver$client

# or for Firefox
 driver <- rsDriver(browser = c("firefox"), port = 3799L)
 
# Download Equity Bhavcopy zip file
bhavs("03012000", 2)

# Close the Browser
remDr$close()

```

## Example 8. RSelenium to Download F&O Bhavcopy
``` r
library(nser)
library(RSelenium)

# Start a selenium server and browser
# For Google Chrome (Update Chrome to latest version)

 driver <- rsDriver(browser = c("chrome"), port = 3163L, chromever = "91.0.4472.101")
 remDr <- driver$client

# or for Firefox
 driver <- rsDriver(browser = c("firefox"), port = 3799L)
 
# Download Equity Bhavcopy zip file
bhavfos("03012000", 2)

# Close the Browser
remDr$close()

```

## Example 9. NSE Treemap 
``` r 
library(nser)
# NIFTY 50 stocks
nsetree()

# F&O stocks
nsetree("fo")
```

## Example 10. NSE NIFTY50 Option chain 
``` r 
library(nser)
optnifty()
```

## Example 11. NSE NIFTY50 Option chain 
``` r 
library(nser)
optbanknifty()
```
